CS222 Project Proposal

### 2019-12-09 proposal/proposal.tex
set up project structure

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
% \documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
% \documentclass[acmsmall]{acmart}\settopmatter{}

@@

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{xcolor}
\usepackage{listings}
\lstset{
  basicstyle=\fontsize{9}{10}\selectfont\ttfamily,
  numbers=left,
  numberstyle= \tiny,
  keywordstyle= \color{ blue!70},
  commentstyle= \color{red!50!green!50!blue!50},
  frame=single,
  rulesepcolor= \color{ red!20!green!20!blue!20} ,
  escapeinside=``,
  xleftmargin=1.5em,xrightmargin=0em, aboveskip=1em,
  framexleftmargin=2em,
  showstringspaces=false,
  showtabs=false,
  breaklines=true
}
\lstdefinelanguage{Solidity}
{
  morekeywords={contract, mapping, address, uint, private, function, public, if, payable},
  morecomment=[l]{//},
  morestring=[b]"
}

@@

@@

@@

%% Title information
\title[]{NO TITLE}         %% [Short Title] is optional;
%% when present, will be used in
%% header instead of Full Title.
%\titlenote{ }             %% \titlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  The abstract \dots
\end{abstract}

@@

\section{Introduction}
The introduction \dots

\section{Body}
The body \dots

\section{Related Work}
The related work \dots

\section{Conclusion}
The conclusion \dots

% Acknowledgments

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
% \documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
\documentclass[acmsmall,nonacm]{acmart}\settopmatter{}

@@

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{xcolor}
\usepackage{listings}
\lstset{
  basicstyle=\fontsize{8}{10}\selectfont\ttfamily,
  numbers=left,
  numberstyle= \tiny,
  keywordstyle= \color{ blue!70},
  commentstyle= \color{red!50!green!50!blue!50},
  frame=single,
  rulesepcolor= \color{ red!20!green!20!blue!20} ,
  escapeinside=``,
  xleftmargin=1.5em,xrightmargin=0em, aboveskip=1em,
  framexleftmargin=2em,
  showstringspaces=false,
  showtabs=false,
  breaklines=true
}
\lstdefinelanguage{Solidity}
{
  morekeywords={contract, mapping, address, uint, private, function, public, if, payable},
  morecomment=[l]{//},
  morestring=[b]"
}

% \usepackage{biblatex}

@@

\usepackage{caption}

@@

% \usepackage[style=authoryear-comp]{biblatex}
% \DeclareLabeldate[online]{%
%   \field{date}
%   \field{year}
%   \field{eventdate}
%   \field{origdate}
%   \field{urldate}
% }
% \DeclareLabeldate{\field{date}\field{eventdate} \field{origdate}\literal{nodate}}

% \DefineBibliographyStrings{english}{%
% nodate = {\ifboolexpr{test{\ifentrytype{misc1}} or test{\ifentrytype{misc5}}}{}{o\adddot D\adddot}},
% }

@@

%% Title information
\title[]{CS222 Project Proposal}         %% [Short Title] is optional;
%% when present, will be used in
%% header instead of Full Title.

@@

% %% Abstract
% %% Note: \begin{abstract}...\end{abstract} environment must come
% %% before \maketitle command
% \begin{abstract}
% 	Text of abstract \ldots
% \end{abstract}

@@

% xyc, until the last
\section{Introduction}

% xyc
\section{Problem Description}

% xzy
\section{Problem Formulation}

% zxy
\section{Related Work}

%% Acknowledgments
